Painting with Triangles

### 2014-04-21 paper.tex
Minor tweak to remove dangling line.
foo

\begin{CRcatlist}
  \CRcat{I.3.4}{Computer Graphics}{Graphics Utilities}{Paint systems}
  \CRcat{I.3.6}{Computer Graphics}{Methodology and Techniques}{Graphics data structures and data types}
\end{CRcatlist}

@@

TrianglePainter reduces the barrier to creating vector graphics by enabling a painting-like interface, with support for sharp and smooth edges. This in turn allows 
artists to focus on the painting and not the way in which they paint, while still 
getting the benefits of vector graphics. We demonstrate our method by creating digital paintings with a 
range of effects and resolutions, including zoom factors of up to 500,000:1 with an effective resolution
of an image with more than $10^{17}$ pixels.

>>>>

\ignorethis{
\begin{CRcatlist}
  \CRcat{I.3.4}{Computer Graphics}{Graphics Utilities}{Paint systems}
  \CRcat{I.3.6}{Computer Graphics}{Methodology and Techniques}{Graphics data structures and data types}
\end{CRcatlist}
}

@@

TrianglePainter reduces the barrier to creating vector graphics by enabling a painting-like interface, with support for sharp and smooth edges. This in turn allows 
artists to focus on the painting and not the way in which they paint, while still 
getting the benefits of vector graphics. We demonstrate our method by creating digital paintings with a 
range of effects and resolutions, including zoom factors of up to 500,000:1 which implies an effective 
resolution equivalent to an image with more than $10^{17}$ pixels.
